### 2024-01-05 paper/si_sections/2_ml.tex
fix table formats (to be finished)

% Supplementary Table 15
\begin{table}[h]
    \centering
    \begin{tabular}{lr}
      \hline
      Elementary Descriptors	Electronic Descriptors
      \hline
      R	atomic radius	α, β, γ	lattice parameters
      Eea	electron affinity	ΦDFT	DFT calculated work function
      Φ	work function	Evac	vacuum level
      XAllen, ΧP, ΧRevP	electronegativity in Allen, Pauling and revised Pauling scales	Eg, Eg↑, Eg↓	average, spin-up and spin-down band gaps
      Ar	relative atomic mass	ed	number of d-electrons
      Ei	ionisation energy	δεd↑	d-band centre (spin-up)
      G	group number	Wd	d-band width
      P	period number	eBader	Bader charge
      V	number of valence electrons
      \hline
    \end{tabular}
    \caption{Notations for elementary descriptors and electronic descriptors}
    \label{si_table15}
\end{table}

@@

% Supplementary Table 16
\begin{table}[h]
    \centering
    \begin{tabular}{lr}
      \hline
      Hyperparameter	Search space	Description
      \hline
      learningRate	[10-4, 10-2], logscale	Learning rate of Adam optimiser
      dropoutRate	[0, 1]	Dropout rate
      root_fc0	128, 256, 512	Output dimensionality of 1st fully connected layer in root
      root_fc1	256, 512, 1024, 2048	Output dimensionality of 2nd fully connected layer in root
      root_act	"tanh", "relu", "sigmoid"	Activation function of fully connected layers in root
      kernelSize	[2, 32]	Width of convolution window
      numFilters	[8, 64]	Number of filters in the convolution
      numConvLayers	[1, 16]	Number of convolution layers
      numConvBlocks	[1, 16]	Number of convolution blocks
      br_fc0	16, 32, 64, 128, 256, 512	Output dimensionality of 1st fully connected layer in branch
      br_fc1	8, 16, 32, 64, 128, 256	Output dimensionality of 2nd fully connected layer in branch
      br_act	"tanh", "relu", "sigmoid"	Activation function of fully connected layers in branch
      \hline
    \end{tabular}
    \caption{The hyperparameter searching space}
    \label{si_table16}
\end{table}

% Supplementary Table 17
\begin{table}[h]
    \centering
    \begin{tabular}{lr}
      \hline
      Hyperparameter	Optimal value	Description
      \hline
      learningRate	10-3	Learning rate of Adam optimiser
      dropoutRate	0.3	Dropout rate
      root_fc0	256	Output dimensionality of 1st fully connected layer in root
      root_fc1	512	Output dimensionality of 2nd fully connected layer in root
      root_act	“relu”	Activation function of fully connected layers in root
      kernelSize	10	Width of convolution window
      numFilters	17	Number of filters in the convolution
      numConvLayers	3	Number of convolution layers
      numConvBlocks	1	Number of convolution blocks
      br_fc0	256	Output dimensionality of 1st fully connected layer in branch
      br_fc1	128	Output dimensionality of 2nd fully connected layer in branch
      br_act	“tanh”	Activation function of fully connected layers in branch
      \hline
    \end{tabular}
    \caption{Optimal hyperparameters identified with Hyperband algorithm}
    \label{si_table17}
\end{table}

% Supplementary Table 18
\begin{table}[h]
    \centering
    \begin{tabular}{lr}
      \hline
      Adsorbate	Original dataset (eV)	Augmented dataset (eV)
      \hline
      CO2	0.0447	0.0336
      COOH	0.0436	0.0581
      CO	0.0402	0.0402
      CHO	0.0614	0.0778
      CH2O	0.0553	0.0632
      OCH3	0.0605	0.0636
      O	0.1135	0.1081
      OH	0.0547	0.0602
      H	0.0703	0.0646
      \hline
    \end{tabular}
    \caption{Prediction mean absolute errors of the CNN model}
    \label{si_table18}
\end{table}
Note. The same CNN model, trained on the augmented dataset, was used for all predictions. The term “Original dataset” refers to evaluations conducted on the original dataset without any augmented data; it does not imply the use of a different CNN model trained solely on the original dataset. Similarly, “Augmented dataset” refers to evaluations on the dataset with both original data and augment data, not a distinct model.

>>>>

% Supplementary Table 15
% TODO: buggy format
\begin{table}[h]
  \centering
  \begin{tabular}{p{3cm} p{11cm}}
    \hline
    \textbf{Elementary Descriptors} & \textbf{Electronic Descriptors} \\
    \hline
    R                 & atomic radius \quad α, β, γ & lattice parameters \\
    Eea               & electron affinity \quad ΦDFT & DFT-calculated work function \\
    Φ                 & work function \quad Evac & vacuum level \\
    XAllen, ΧP, ΧRevP & electronegativity in Allen, Pauling, and revised Pauling scales \quad Eg, Eg↑, Eg↓ & average, spin-up, and spin-down band gaps \\
    Ar                & relative atomic mass \quad ed & number of d-electrons \\
    Ei                & ionization energy \quad δεd↑ & d-band center (spin-up) \\
    G                 & group number \quad Wd & d-band width \\
    P                 & period number \quad eBader & Bader charge \\
    V                 & number of valence electrons \\
    \hline
  \end{tabular}
  \caption{Notations for elementary descriptors and electronic descriptors}
  \label{si_table15}
\end{table}

@@

% Supplementary Table 16
\begin{table}[h]
  \centering
  \begin{tabular}{lrp{5.5cm}}
    \hline
    \textbf{Hyperparameter} & \textbf{Search Space}                             & \textbf{Description}            \\
    \hline
    learningRate  & [10\textsuperscript{-4}, 10\textsuperscript{-2}], log scale & Learning rate of Adam optimizer \\
    dropoutRate   & [0, 1]                    & Dropout rate                                                      \\
    root\_fc0     & 128, 256, 512             & Output dimensionality of 1st fully connected layer in root        \\
    root\_fc1     & 256, 512, 1024, 2048      & Output dimensionality of 2nd fully connected layer in root        \\
    root\_act     & "tanh", "relu", "sigmoid" & Activation function of fully connected layers in root             \\
    kernelSize    & [2, 32]                   & Width of the convolution window                                   \\
    numFilters    & [8, 64]                   & Number of filters in the convolution                              \\
    numConvLayers & [1, 16]                   & Number of convolution layers                                      \\
    numConvBlocks & [1, 16]                   & Number of convolution blocks                                      \\
    br\_fc0       & 16, 32, 64, 128, 256, 512 & Output dimensionality of 1st fully connected layer in branch      \\
    br\_fc1       & 8, 16, 32, 64, 128, 256   & Output dimensionality of 2nd fully connected layer in branch      \\
    br\_act       & "tanh", "relu", "sigmoid" & Activation function of fully connected layers in branch           \\
    \hline
  \end{tabular}
  \caption{The hyperparameter search space}
  \label{si_table16}
\end{table}

% Supplementary Table 17
\begin{table}[h]
  \centering
  \begin{tabular}{lrp{5.5cm}}
    \hline
    \textbf{Hyperparameter}   & \textbf{Optimal Value} & \textbf{Description}                \\
    \hline
    learningRate  & $10^{-3}$ & Learning rate of Adam optimizer                              \\
    dropoutRate   & 0.3       & Dropout rate                                                 \\
    root\_fc0     & 256       & Output dimensionality of 1st fully connected layer in root   \\
    root\_fc1     & 512       & Output dimensionality of 2nd fully connected layer in root   \\
    root\_act     & "relu"    & Activation function of fully connected layers in root        \\
    kernelSize    & 10        & Width of convolution window                                  \\
    numFilters    & 17        & Number of filters in the convolution                         \\
    numConvLayers & 3         & Number of convolution layers                                 \\
    numConvBlocks & 1         & Number of convolution blocks                                 \\
    br\_fc0       & 256       & Output dimensionality of 1st fully connected layer in branch \\
    br\_fc1       & 128       & Output dimensionality of 2nd fully connected layer in branch \\
    br\_act       & "tanh"    & Activation function of fully connected layers in branch      \\
    \hline
  \end{tabular}
  \caption{Optimal hyperparameters identified with Hyperband algorithm}
  \label{si_table17}
\end{table}

% Supplementary Table 18
\begin{table}[h]
  \centering
  \begin{tabular}{lrr}
    \hline
    \textbf{Adsorbate} & \textbf{Original dataset (eV)} & \textbf{Augmented dataset (eV)} \\
    \hline
    CO$_2$  & 0.0447 & 0.0336 \\
    COOH    & 0.0436 & 0.0581 \\
    CO      & 0.0402 & 0.0402 \\
    CHO     & 0.0614 & 0.0778 \\
    CH$_2$O & 0.0553 & 0.0632 \\
    OCH$_3$ & 0.0605 & 0.0636 \\
    O       & 0.1135 & 0.1081 \\
    OH      & 0.0547 & 0.0602 \\
    H       & 0.0703 & 0.0646 \\
    \hline
  \end{tabular}
  \caption{Prediction mean absolute errors of the CNN model}
  \label{si_table18}
\end{table}

Note. The same CNN model, trained on the augmented dataset, was used for all predictions. The term “Original dataset” refers to evaluations conducted on the original dataset without any augmented data; it does not imply the use of a different CNN model trained solely on the original dataset. Similarly, “Augmented dataset” refers to evaluations on the dataset with both original data and augment data, not a distinct model.

### 2024-01-05 paper/si_sections/3_others.tex
fix table formats (to be finished)

% Supplementary Table 19
\begin{table}[h]
    \centering
    \begin{tabular}{lr}
      \hline
      Name	Version	Build	Channel
      \hline
      conda	4.13.0	py39h06a4308_0	anaconda
      cuda-nvcc	11.8.89	0	nvidia
      cuda-toolkit	11.8.0	0	nvidia
      cudatoolkit	11.6.0	habf752d_9	nvidia
      ipykernel	6.9.1	py39h06a4308_0	anaconda
      ipython	7.34.0	pypi_0	pypi
      jupyter_client	7.2.2	py39h06a4308_0	anaconda
      jupyterlab	3.4.4	py39h06a4308_0	anaconda
      keras	2.9.0	pypi_0	pypi
      keras-preprocessing	1.1.2	pypi_0	pypi
      keras-tuner	1.3.5		pypi
      matplotlib	3.5.1	py39h06a4308_1	anaconda
      numpy	1.22.4	pypi_0	pypi
      pandas	1.3.4	py39h8c16a72_0	anaconda
      python	3.9.12	h12debd9_1	anaconda
      scikit-learn	1.1.1	py39h6a678d5_0	anaconda
      scipy	1.8.1	py39hddc5342_3	conda-forge
      tensorboard	2.9.1	pypi_0	pypi
      tensorflow	2.9.3	pypi_0	pypi
      tensorflow-gpu	2.9.3	pypi_0	pypi
      xlrd	2.0.1	pyhd3eb1b0_0	anaconda
      yaml	0.2.5	h7b6447c_0	anaconda
      \hline
    \end{tabular}
    \caption{Core packages in deep learning environment}
    \label{si_table19}
\end{table}
Note. The complete list of packages is provided along with the source code.

@@

% Supplementary Table 20
\begin{table}[h]
    \centering
    \begin{tabular}{lr}
      \hline
      Name	Version	Build	Channel
      \hline
      bokeh	3.2.2	pypi_0	pypi
      colorcet	3.0.1	pypi_0	pypi
      heatmapz	0.0.4	pypi_0	pypi
      keras	2.13.1	pypi_0	pypi
      keras-tuner	1.3.5	pypi_0	pypi
      matplotlib	3.7.2	pypi_0	pypi
      numpy	1.24.3	pypi_0	pypi
      pandas	2.0.3	pypi_0	pypi
      python	3.11.4	hb885b13_0
      pyyaml	6.0.1	pypi_0	pypi
      scikit-learn	1.3.0	pypi_0	pypi
      scipy	1.11.1	pypi_0	pypi
      seaborn	0.12.2	pypi_0	pypi
      tensorboard	2.13.0	pypi_0	pypi
      tensorflow	2.13.0	pypi_0	pypi
      tensorflow-macos	2.13.0	pypi_0	pypi
      \hline
    \end{tabular}
    \caption{Core packages in data analysis and visualization environment}
    \label{si_table20}
\end{table}
Note. The complete list of packages is provided along with the source code.

>>>>

% Supplementary Table 19
\begin{table}[h]
  \centering
  \begin{tabular}{l l l l}
    \hline
    Name                & Version & Build          & Channel     \\
    \hline
    conda               & 4.13.0  & py39h06a4308_0 & anaconda    \\
    cuda-nvcc           & 11.8.89 & 0              & nvidia      \\
    cuda-toolkit        & 11.8.0  & 0              & nvidia      \\
    cudatoolkit         & 11.6.0  & habf752d_9     & nvidia      \\
    ipykernel           & 6.9.1   & py39h06a4308_0 & anaconda    \\
    ipython             & 7.34.0  & pypi_0         & pypi        \\
    jupyter\_client     & 7.2.2   & py39h06a4308_0 & anaconda    \\
    jupyterlab          & 3.4.4   & py39h06a4308_0 & anaconda    \\
    keras               & 2.9.0   & pypi_0         & pypi        \\
    keras-preprocessing & 1.1.2   & pypi_0         & pypi        \\
    keras-tuner         & 1.3.5   &                & pypi        \\
    matplotlib          & 3.5.1   & py39h06a4308_1 & anaconda    \\
    numpy               & 1.22.4  & pypi_0         & pypi        \\
    pandas              & 1.3.4   & py39h8c16a72_0 & anaconda    \\
    python              & 3.9.12  & h12debd9_1     & anaconda    \\
    scikit-learn        & 1.1.1   & py39h6a678d5_0 & anaconda    \\
    scipy               & 1.8.1   & py39hddc5342_3 & conda-forge \\
    tensorboard         & 2.9.1   & pypi_0         & pypi        \\
    tensorflow          & 2.9.3   & pypi_0         & pypi        \\
    tensorflow-gpu      & 2.9.3   & pypi_0         & pypi        \\
    xlrd                & 2.0.1   & pyhd3eb1b0_0   & anaconda    \\
    yaml                & 0.2.5   & h7b6447c_0     & anaconda    \\
    \hline
  \end{tabular}
  \caption{Core packages in the deep learning environment}
  \label{si_table19}
\end{table}
Note. The complete list of packages is provided along with the source code.

@@

% Supplementary Table 20
\begin{table}[h]
  \centering
  \begin{tabular}{l l l l}
    \hline
    Name             & Version & Build      & Channel \\
    \hline
    bokeh            & 3.2.2   & pypi_0     & pypi    \\
    colorcet         & 3.0.1   & pypi_0     & pypi    \\
    heatmapz         & 0.0.4   & pypi_0     & pypi    \\
    keras            & 2.13.1  & pypi_0     & pypi    \\
    keras-tuner      & 1.3.5   & pypi_0     & pypi    \\
    matplotlib       & 3.7.2   & pypi_0     & pypi    \\
    numpy            & 1.24.3  & pypi_0     & pypi    \\
    pandas           & 2.0.3   & pypi_0     & pypi    \\
    python           & 3.11.4  & hb885b13_0 &         \\
    pyyaml           & 6.0.1   & pypi_0     & pypi    \\
    scikit-learn     & 1.3.0   & pypi_0     & pypi    \\
    scipy            & 1.11.1  & pypi_0     & pypi    \\
    seaborn          & 0.12.2  & pypi_0     & pypi    \\
    tensorboard      & 2.13.0  & pypi_0     & pypi    \\
    tensorflow       & 2.13.0  & pypi_0     & pypi    \\
    tensorflow-macos & 2.13.0  & pypi_0     & pypi    \\
    \hline
  \end{tabular}
  \caption{Core packages in the data analysis and visualization environment}
  \label{si_table20}
\end{table}
Note. The complete list of packages is provided along with the source code.
